Untrusted B2B Collaboration using the Blockchain

### 2018-07-09 paper/paper.tex
Fix merge

\begin{document}
%
\title{Untrusted B2B Collaboration using the Blockchain}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Jonas Beyer \and
Philipp Otto\and
S\"oren Tietb\"ohl}
%
\authorrunning{J. Beyer et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Hasso-Plattner-Institut f\"ur Digital Engineering gGmbH, Prof.-Dr.-Helmert-Str. 2-3, Potsdam 14482, Germany\\
\email{\{jonas.beyer,philipp.otto2,soeren.tietboehl\}@student.hpi.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Blockchain technology enables untrusting parties to have trusted communication. We use this to implement a conversion of BPM choreographies to smart contracts on the Ethereum Blockchain.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}

@@

What is BPMN?
What is Blockchain?
What problems are there with BPMN that can be solved with Blockchain?
What approaches exist currently (Caterpillar \cite{lopez2017caterpillar}, Untrusted paper \cite{weber2016untrusted})
What is our general Idea?
What are our results? (briefly)

>>>>

\begin{document}
%
\title{Untrusted B2B Collaboration using the Blockchain}
%
%
\author{Jonas Beyer \and
Philipp Otto\and
S\"oren Tietb\"ohl}
%
\authorrunning{J. Beyer et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Hasso-Plattner-Institut, Potsdam, Germany\\
\email{\{jonas.beyer,philipp.otto2,soeren.tietboehl\}@student.hpi.de}}
%
\maketitle % typeset the header of the contribution
%
\begin{abstract}
Lack of trust between communication partners is one of the major issues companies face when implementing business processes in a cross-organizational setting.
Blockchain is an emerging technology that enables decentralization and distribution of state without the need for a trusted central instance.
This allows for consensus in communication between otherwise untrusting parties.
In this paper we introduce Armadillo, an open-source prototype implementation for realizing business process choreographies using the Ethereum blockchain.
We present a user interface for connecting business processes with blockchain calls, as well as an underlying smart contract structure for inter-process communication.

\keywords{Blockchain \and Business Processes \and Ethereum \and Choreography \and Smart Contract \and BPMN}
\end{abstract}
%
%
%
\section{Introduction}

@@

% What is BPMN?
The Business Process Model Notation (BPMN) enables detailed documentation of business processes. This is used to realize complex inter-business processes which involve vast communication structures. One common problem is that within these processes the parties have to trust each other.
% What is Blockchain?

With the increasing spread of Blockchain technology, this problem could be rectified.
A Blockchain is a decentralized information-storage network. Information is stored in blocks, which are chained together via cryptograhic means. This means, that many participants can agree on a common public state of information without trusting each other. This technology is commonly used to realize virtual currencies, also called cryptocurrencies.
Ethereum is one implementation of the Blockchain concept, and it realizes a key feature called smart contracts.
Smart contracts are small programs, which are ran by the Blockchain network. They have very limited processing power, but they enable the execution of code which has a commonly known state.

%What problems are there with BPMN that can be solved with Blockchain?
The problem of needing to trust each other when collaborating in a business process can be addressed by applying the benefits of blockchain technology. The Blockchain be used in several ways to facilitate trusted communication between untrusted parties.

% What approaches exist currently (Caterpillar \cite{lopez2017caterpillar}, Untrusted paper \cite{weber2016untrusted})
Current approaches aim to convert the functionality of traditional BPMN Engines to smart contracts on the Ethereum Blockchain.

Caterpillar~\cite{lopez2017caterpillar} features the implementation of most common BPMN elements. It enables the transformation of BPMN Models to smart contracts, which can be deployed and executed on the Blockchain.

Weber et al.~\cite{weber2016untrusted} realize Orchestrations on the Blockchain.

%What is our general Idea?
We want to expand on the work of Weber et al. and implement true choreographies. In their current approach they are using one central smart contract called a mediator / monitor which manages the Orchestration state.
We will have a set of smart contracts for every party, which will then communicate with each other to realize the choreography.
%What are our results? (briefly)
